upwell_IDX

### 2019-08-13 upwell_IDX.Rmd
progress

```{r}
library(tidyverse)
library(ggplot2)
library(circular)
# devtools::install_github("robwschlegel/coastR")
library(coastR)
library(gridExtra)
library(dplyr)
library(geosphere)
```

@@

# Determining the upwelling indeces by changing the angle for each of the sites

```{r}

wind_angle <- wind_daily %>% 
  dplyr::rename(site = sites) %>% 
  left_join(south_africa_away_wide[,c(2,21)], by = "site") %>% 
  dplyr::rename(coast_angle = heading)

##### Do this
wind_UI <- wind_daily %>% 
  mutate(ui.saws = mean_speed * (cos(dir_circ - coast_angle))) %>% 
  drop_na

index <- wind_UI %>% 
  group_by(sites) %>% 
  select("date", "ui.saws") %>% 
  mutate(saws.condition = ifelse(ui.saws < 12.5, "upwelling"))

@@

# Visualisiing the data

```{r}
plot1 <- ggplot(data = index, aes(x = date, y = ui.saws)) +
  geom_line() +
  facet_wrap(~sites, ncol = 1) +
  geom_area(aes( fill = saws.condition)) +
  theme_grey()
plot1
```

@@

```{r}
match_func <- function(df){
  match <- SACTN_MCS_clims  %>% 
  left_join(df, by = c("site", "t")) %>% 
  na.trim()
  return(match)
}

index <- index %>% 
  dplyr::rename(site = sites) %>% 
  dplyr::rename(t = date)

match <- match_func(df = index)

upwell_MCS <- ggplot(data = match, aes(x = t, y = ui.saws)) +
  geom_line() +
  geom_point(data = filter(match, event == TRUE), colour = "navy") +
  geom_rug(data = filter(match, saws.condition == "upwelling"), sides = "b") +
  scale_x_date(expand = c(0, 0)) +
  facet_wrap(~site, ncol = 1) +
  theme_grey() +
  labs(y = "Temperature (°C)", x = NULL)
upwell_MCS

>>>>

```{r}
library(tidyverse)
library(ggplot2)
library(circular)
# devtools::install_github("robwschlegel/coastR")
library(coastR)
library(gridExtra)
library(dplyr)
library(geosphere)
library(heatwaveR)
```

@@

```{r}
UI_angle <- wind_daily %>% 
  dplyr::rename(site = sites) %>% 
  left_join(south_africa_away_wide[,c(2,21)], by = "site") %>% 
  dplyr::rename(coast_angle = heading) %>% 
  mutate(ui.saws = mean_speed * (cos(dir_circ - coast_angle))) %>% # Calculated perpendicular angle for each of the sites. Not necessary
  drop_na

# index <- wind_UI %>%
#   group_by(site) %>%
#   select("date", "ui.saws") %>%
#   mutate(saws.condition = ifelse(ui.saws < 12.5, "upwelling"))

wind_UI <- wind_daily %>% 
  mutate(ui.saws = mean_speed * (cos(dir_circ - 160))) %>% # 160 is angle perpendicular to the west coast of SA (See paper Fielding and Davis pg 182)
  drop_na

# Results obtained from UI_angle (Using the perpendicular angle for each site) and the results of wind_UI at -160 (angle of the west coast) appears to be the same
```

# Exceedence function heatwaveR - This is done to determine the consecutive number of days at or above what the UI value is ment to be

```{r}
# Loading the insitu temperature data along the wc
load("Data/SACTN_US.RData")

# exceedance <-
#   function(data,
#            x = t,
#            y = temp,
#            threshold,
#            below = FALSE,
#            minDuration = 5,
#            joinAcrossGaps = TRUE,
#            maxGap = 2,
#            maxPadLength = 3)

# Upwelling temperature threshold 12.4 / 30th percentile

SACTN_upwell <- SACTN_US %>% 
  dplyr::rename(t = date) %>%
  group_by(site) %>%
  nest() %>% 
  mutate(exceed = purrr::map(data, exceedance, threshold = 12.4, below = TRUE))

# SACTN_upwell_transform <- as.data.frame(read.zoo(transform( SACTN_upwell, Date = as.POSIXct(t) ), FUN = identity ))

@@

@@

```{r}
# match_func <- function(df){
#   match <- SACTN_MCS_clims  %>% 
#   left_join(df, by = c("site", "t")) %>% 
#   na.trim()
#   return(match)
# }
# 
# index <- index %>% 
#   dplyr::rename(site = sites) %>% 
#   dplyr::rename(t = date)
# 
# match <- match_func(df = index)
# 
# upwell_MCS <- ggplot(data = match, aes(x = t, y = ui.saws)) +
#   geom_line() +
#   geom_point(data = filter(match, event == TRUE), colour = "navy") +
#   geom_rug(data = filter(match, saws.condition == "upwelling"), sides = "b") +
#   scale_x_date(expand = c(0, 0)) +
#   facet_wrap(~site, ncol = 1) +
#   theme_grey() +
#   labs(y = "Temperature (°C)", x = NULL)
# upwell_MCS
